Pyro -Velocity: Probabilistic RNA Velocity inference from single-cell data

### 2024-08-20 reproducibility/manuscript/v2.tex
chore(manuscript): update v2 diff file

\raggedbottom
\usepackage{nameref}
\usepackage{placeins}
\usepackage{framed}
\allowdisplaybreaks
\makeatletter
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{plain}
\@ifundefined{c@chapter}{\newfloat{suppfig}{h}{loextfig}}{\newfloat{suppfig}{h}{loextfig}[chapter]}
\floatname{suppfig}{Extended Data Fig.}
\newcommand*\listofsuppfigs{\listof{suppfig}{List of Extended Data Figures}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

>>>>

\raggedbottom
\usepackage{nameref}
\usepackage{placeins}
\allowdisplaybreaks
\makeatletter
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{plain}
\@ifundefined{c@chapter}{\newfloat{suppfig}{h}{loextfig}}{\newfloat{suppfig}{h}{loextfig}[chapter]}
\floatname{suppfig}{Extended Data Fig.}
\newcommand*\listofsuppfigs{\listof{suppfig}{List of Extended Data Figures}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\subsection{Cell fate uncertainty
estimation}\label{sec-methods-fate-uncertainty}

Pyro -Velocity evaluates cell fate uncertainty using four statistics.
The first is the uncertainty of shared time, which is evaluated using
the standard deviation of posterior samples of \(t_c\) for each cell.
The second statistic is the angular standard deviation
\citep{Berens2009-fu} across posterior samples of the velocity-based
vector field. The value of this statistic was mapped linearly to the
range \([0, 360]\) for interpretability. The third statistic is the
Rayleigh test \citep{The-Astropy-Collaboration2022-aw} for posterior
samples of the velocity-based vector fields for each cell, whose
p-values have been corrected for multiple tests using Benjamini-Hochberg
FDR methods; if FDR is less than \(0.05\), the cell is considered to
have one statistically significant future direction. The second and
third circular statistics were implemented using the Astropy package
(\texttt{v5.1}) \citep{The-Astropy-Collaboration2022-aw}. The last
statistic is state uncertainty which evaluates the mean Euclidean
distance between posterior mean and posterior samples of the raw read
count prediction for each cell \begin{align*}
\frac{1}{N} \sum_{i} \sqrt{\sum_{g} \left(x_{icg} - \frac{1}{N}\sum_i x_{icg}\right)^2}.
\end{align*}
